%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithOutColon}[1]{
	\item\small{
		{ #1 \vspace{-2pt}}
	}
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
	\vspace{-1pt}
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textit{\small#1} & \textit{\small #2} \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Shaily Mishra}} & Email : \href{mailto:shaily.mishra30@gmail.com}{shaily.mishra30@gmail.com}\\
   & Mobile : +91-962-490-5555 \\ & Medium  : https://medium.com/@iammethod
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {School of Engineering and Applied Science}{Ahmedabad, Gujarat, India}
      {Bachelor of Technology in Information and Communication Technology;  GPA: 3.01/4.33}{July. 2013 -- May. 2017}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Argusoft}{Gandhinagar, Gujarat, India}
      {Programmer Analyst}{June 2017 - Present}
      \resumeItemListStart
		\resumeItem{Campaign Management Platform}
		  {The platform is an omni-channel, that manages inbound and outbound campaign
		  	flows for the subscribers throughout their lifecycle.
		  	Initially it started as a frontend application that would provided UI for user to interact with the backend services. Later it become an application which was completely dynamic, meaning client can create modules according to their product. Configure all activity related to the campaign.
		  	I was the Lead Frontend Developer. The frontend was made in Angular 2.x+. It involved resturturizing the whole project, to make everything dynamic. It also included migration of project as lastest version of angular were released i.e from Angular 2 to Angular 7. Also was responsible for unit test cases, e2e test cases and documentation of the project.
	  	}
        \resumeItem{Survey Tool}
          {Working on platform through which user can create a smart survey having Branching, Piping, Looping, Response Value. Technologies used - ExpressJS for Backend Restful APIs. Angular 7 for Frontend. Postgres for database. Theme of frontend was design using angular material I worked as Frontend Lead Developer : from setting up the project structure to deploying the project. Currently working on user athentication, authorization and dynamic forms using material and reactive forms.}
        \resumeItem{National Sports Talent Search (Sports Authority of India)}
          {
           This application is meant to reach every corner of India and to facilitate the talented sportsperson to
          register with Sports Authority of India to get the benefits of different schemes offered by it.
          Nativescript was used to create hybrid app for Android and IOS. I was part of the frontend team, involved in creating application structure, interactation with client to define the structure of APIs and communication protocols etc.
          Worked on production deployment on Play Store and Apple Store for the application.
          }
      \resumeItemListEnd
    \resumeSubSubheading
      {Trainee}{Jan 2017 - May 2017}
      \resumeItemListStart
        \resumeItem{Web Technologies}
          {Core JAVA, Servlets, JSP, Spring MVC, JBDC, JPA, Restful APIs, Javascript, Angular 1.x , Angular 2.x+, NodeJs }
           \resumeItem{Databases}
          {MySQl, PostGres, MongoDB }
           \resumeItem{Testing Framework}
{Protractor, Karma, Jasmine }
        \resumeItem{Employee Department Management}
          {Created the platform as part of training. Frontend : Angular 2.x+, Backend : ExpressJs, Database : MySQL }
      \resumeItemListEnd

    \resumeSubheading
      {School of Engineering and Applied Science}{Ahmedabad , Gujarat, India}
      {Teaching Assistant - Linear Algebra}{August 2016 - Dec 2016, }
      \resumeItemListStart
        \resumeItemWithOutColon
          {My job involved preparing weekly assignments with 10 problems along with solutions, conducting a class for assignment solving, checking assignments for 120 students, responsible for marks and attendance management, Evaluating Midsem and Endsem papers, Assisted students in projects and attending all lectures. The course had two TA. Responsibilty was divided among us. Book followed was Linear Algebra  by Gilbert Strang }
      \resumeItemListEnd
          \resumeSubSubheading
  {Teaching Assistant - Calculus and Differential Equations}{July 2014 - Nov 2014, }
 \resumeItemListStart
\resumeItemWithOutColon
{My job involved weekly attending class for assignment solving session, assisting professor in problem solving classes,  Supervisoring class test, evaluating them and assisting student in course project. Book followed was Advanced Engineering Mathematics by Jain and Iyengar }
\resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Game Theory - Nash Equilibrium}
  {Creating Mind Map and Summary for ‘Beyond Myopic Best Response (in Cournot Competition)’ paper. Further, analysing the worst case equilibria, minimizing the costs (both routing and link creation cost) for topologies having newer nodes .}  
 
  \resumeSubItem{Compression and Encryption }
{Implementation of entropy based lossless compression - Huffman,Adaptive Huffman and Arithmetic. Implementation of Linear Block code - Hamming Code and Low Density Parity Code.} 


 
    \resumeSubItem{CPU Scheduling Algorithm}
      {Implementation of process scheduling algorithms : FCFS,RR,SPN using shell script -through signal handling and pthreads. LR Parser acted as our processor. Text file containing arithmetic equations were processes. 
      }
    \resumeSubItem{Event Ticket Booking Portal}
{Design and Implemented Event Ticket Booking database. Making of ERD, Relations, ERD to Relations, Normalisation. And wrote more than 200+ SQL Queries. Also created procedures,triggers and transactions.
}
    \resumeSubItem{Spell Checker}
      {Java Program with database of 5k words using trie tree data structure}

    \resumeSubItem{ALU and Non-pipelined MIPS Processor}
{
Created 32-bit ALU using Logisim and doing hardware optimization. Created a non-pipelined MIPS processor having 5 stages in verilog using Xilinx tool and simulate the processor by creating a test bench using the Xilinx tool.
}

\resumeSubItem{Smart Room}{Make a Working Prototype of Smart Room.Light and fan of a room
	were automated using inputs as the number of people present in the room, temperature and
	light intensity of the room.}

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Extra Articular}
  \resumeSubHeadingListStart
    \resumeSubItem{Dynamos Sport Fest of SEAS}
      {First in 100 m Girls}
    \resumeSubItem{Adani Ahmedabad Marathon}
      {Run for Soldiers. 5km under 45 minutes}
    \resumeSubItem{Himalyan Trek}
      {Deoriatal Chandrashila Peak Trek. Moderate. 4-8 march. Completed the Summit}
  \resumeSubHeadingListEnd


%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
